\documentclass[../main.tex]{subfiles}
\begin{document}
	
\frontmatter
\chapter{The Ugly Truth}
\section{About this Book}

When I set out to write this book, we as a section, were struggling to certify our developers.  For one reason or another, we watched multiple failed attempts at the Basic Service Level Exam (BSLE).  It is our hope that providing extra materials, guidance, and hands-on exercises, we'll be able to reverse this trend.  I don't expect this book to be all encompassing; you won't go from "Zero to Hero".  It should serve as a way to hopefully guide you toward a base level of knowledge within the C programming language.  With that base, we can begin to explore more advanced topics and languages.  

I completely expect this book to have errors.  Please be kind and submit your errata in a pull request.

\section{Who am I}
I am not an expert in C and I don't claim to be.  I knew just enough to pass the exam and writing this book is another way in which I am trying to progress as a developer.  What I do have is a little bit of time between projects and a stack of books beside me that will hopefully assist me in shedding some light on various topics.  Also, I'm in no way an accomplished author.  I can barely speak English even though I've been doing so my whole life.  Prepare yourself mentally for the worst grammar you've ever seen.  When all else fails, focus on the points I'm attempting to make and not on how I'm presenting it.  If all else fails, put in a pull request to help fix my deficiencies.

If you're reading this book after 2020, we are going through a Pandemic.  Yay us!  However, what this has given me is extra time to work on things like this.  Hopefully at least something good comes from it.

\section{Why C}

C is not my favorite language nor do I expect it to be yours.  However, C has been around for a long time and many languages take their roots from it.  Learning C will not only help you understand existing code bases, but will give you insights into and maybe even an appreciation for newer languages.  At the end of the day though, C is a major portion of the BSLE exam and you need to know it in order to pass.

\mainmatter
\end{document}